---
title: "Reproducible document"
author: "Josefine Klakk"
format: html
---

## Basics of R

```{r}
1 + 1
```

## Setup code chunk

```{r setup}
#| message: false
library(tidyverse)
post_meal_data <- read_csv2(
  here::here("data/post-meal-insulin.csv")
)
```

## Showing the data
```{r}
post_meal_data
```

```{r}
glimpse(post_meal_data)
```

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```
@fig-bmi-histo


## About me

- Josefine Klakk 
- The National Centre for Register-based Research, Aarhus University

I am **27 years** old and I am from *Haderslev* in Southern Denmark.

## Simple code
```{r}
3 * 3
```
## Testing for Git
The weather is cold and gray and I miss the sun

## Showing the data

## Exercise: Discrete plots

```{r}
#| fig-cap: "Group"
#| label: fig-group-bar
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```


See @fig-group-bar above for a cool plot!

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = glykemi)) +
  geom_bar()
```


```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Putting two plots side by side

```{r}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```



```{r}
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

```{r side-by-side-figures}
#| label: fig-bmi-group
#| fig-cap: "BMI and glykemi side by side"
#| fig-subcap:
#| - "Distribution of BMI"
#| - "Number of those with glycemia"
#| layout-ncol: 2

ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continuous variables

```{r}
#| fig-cap: "scatterplot showing BMI against AUC of blood glucose"
#| label: fig-bmi-auc-pg 
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) + 
  geom_point() + 
  geom_smooth()
```

## Pushing changes to remote

## Pulling changes locally
